Stateless Model Checking with Data-Race Preemption Points

### 2016-08-17 oopsla-16/implementation.tex
take care of some TODO CAMREADies

{\bf Data races in lock implementations.}
Data race tools in prior work \cite{tsan,portend} recognize the implementations of synchronization primitives to avoid spuriously flagging memory accesses %therein. %resulting from the lock implementation itself.
that implement them.
Assuming that the lock implementation is already correct enables more productive data-race analysis on the rest of the codebase,
% TODO CAMREADY: Cite simsa thesis
while the locks themselves can be verified separately.
%Otherwise, %with testing limited to one execution,
%%even if one wishes to test for lock bugs,
%\revision{a single-pass}~data-race analysis would flag every access pair in the lock implementation. %, requiring human attention to verify.
%However, Iterative Deepening removes the need for human attention to verify them. %can automatically verify a large quantity of data-race candidates as benign.
%While most tests in our evaluation assume correct locks,
We included a mutex test in our evaluation
to showcase \quicksand's ability to verify synchronization primitives with data-race PPs
(\sect{\ref{sec:testsuite}}).
To support this test, we extended \landslide~to
%with an option
optionally make its data race analysis consider accesses from {\tt mutex\_lock()} and {\tt mutex\_unlock()}.
%which we use to test mutexes (\sect{\ref{sec:testsuite}}).
%(Accesses from other synchronization functions, such as {\tt cond\_wait()}, would either be included already, or be protected by an internal mutex.)

>>>>

{\bf Data races in lock implementations.}
Data race tools in prior work \cite{tsan,portend} recognize the implementations of synchronization primitives to avoid spuriously flagging memory accesses %therein. %resulting from the lock implementation itself.
that implement them.
Assuming that the lock implementation is already correct enables more productive data-race analysis on the rest of the codebase,
while the locks themselves can be verified separately \cite{dbug-thesis}.
%Otherwise, %with testing limited to one execution,
%%even if one wishes to test for lock bugs,
%\revision{a single-pass}~data-race analysis would flag every access pair in the lock implementation. %, requiring human attention to verify.
%However, Iterative Deepening removes the need for human attention to verify them. %can automatically verify a large quantity of data-race candidates as benign.
%While most tests in our evaluation assume correct locks,
We included a mutex test in our evaluation
to showcase \quicksand's ability to verify synchronization primitives with data-race PPs
(\sect{\ref{sec:testsuite}}).
To support this test, we extended \landslide~to
%with an option
optionally make its data race analysis consider accesses from {\tt mutex\_lock()} and {\tt mutex\_unlock()}.
%which we use to test mutexes (\sect{\ref{sec:testsuite}}).
%(Accesses from other synchronization functions, such as {\tt cond\_wait()}, would either be included already, or be protected by an internal mutex.)

### 2016-08-17 oopsla-16/soundness.tex
change formatting according to camready author package
take care of some TODO CAMREADies

\subsection{Convergence to total verification}
\label{sec:totalverif}

@@

\subsection{Suppressing ``malloc-recycle'' false positives}
\label{sec:recycle}

@@

\begin{figure}[t]
	\small
\begin{tabular}{rll}
	% TODO: Can cut struct defns for space.
	& \multicolumn{2}{c}{\texttt{struct x \{ int foo; int baz; \} *x;}} \\
	& \multicolumn{2}{c}{\texttt{struct y \{ int bar; \} *y;~~~~~~~~~~}} \\
	\\
	& {\bf Thread 1} & {\bf Thread 2} \\
	1 & \texttt{\hilight{brickred}{x->foo = ...;}} & \\
	2 & \texttt{\hilight{olivegreen}{free}(x);} \\
	3 & & \texttt{\hilight{commentblue}{// x's memory recycled}} \\
	4 & & \texttt{y~=~\hilight{olivegreen}{malloc}(sizeof *y);} \\
	5 & & \texttt{\hilight{commentblue}{// ...initialize...}}\\
	6 & & \texttt{publish(y);} \\
	7 & & \texttt{\hilight{brickred}{y->bar = ...;}} \\
\end{tabular}
\caption{A common execution pattern with {\tt malloc()} that produces false positive data race candidates.}
\label{fig:recycle}
\end{figure}
\begin{figure}[t]
	\small
\begin{tabular}{rll}
	& {\bf Thread 1} & {\bf Thread 2} \\
	1 & \texttt{publish(x);} & \\
	2 & \texttt{\hilight{brickred}{x->foo = ...;}} & \\
	3 & \texttt{\hilight{olivegreen}{free}(x);} \\
	4 & & \texttt{x2 = get\_published\_x();} \\
	5 & & \texttt{\hilight{commentblue}{// x's memory recycled}} \\
	6 & & \texttt{y~=~\hilight{olivegreen}{malloc}(sizeof *y);} \\
	7 & & \texttt{\hilight{brickred}{x2->foo = ...;}} \\
\end{tabular}
	\caption{If a single-pass \revision{Limited HB analysis}~discarded candidates matching the malloc-recycle pattern,
it would miss the bug in this adversarial program.}
\label{fig:recycle-bug}
\end{figure}

@@

\revision{This class of false positive is unique to heap-allocated memory among all ways threads could communicate.
By contrast, global memory has unlimited lifetime,
and message-passing primitives enforce an ordering which precludes the race. %(even under Limited HB).
Finally, note that as long as concurrent {\tt malloc} is implemented with an internal lock,
these false positives are of concern only under a Limited HB analysis (\sect{\ref{sec:overview-dr}}).
Nevertheless,
%our previous proof's
Theorem~\ref{thm:convergence}'s need for the Limited HB definition justifies our choice of it over full HB.
% TODO CAMREADY: Cite the tech report proofs, which I think call out the use of limited HB in the proof more explicitly.
}

>>>>

\subsection{Convergence to Total Verification}
\label{sec:totalverif}

@@

\subsection{Suppressing ``Malloc-Recycle'' False Positives}
\label{sec:recycle}

@@

\begin{figure}[t]
	\small
\begin{tabular}{rll}
	& \multicolumn{2}{c}{\texttt{struct x \{ int foo; int baz; \} *x;}} \\
	& \multicolumn{2}{c}{\texttt{struct y \{ int bar; \} *y;~~~~~~~~~~}} \\
	\\
	& {\bf Thread 1} & {\bf Thread 2} \\
	1 & \texttt{\hilight{brickred}{x->foo = ...;}} & \\
	2 & \texttt{\hilight{olivegreen}{free}(x);} \\
	3 & & \texttt{\hilight{commentblue}{// x's memory recycled}} \\
	4 & & \texttt{y~=~\hilight{olivegreen}{malloc}(sizeof *y);} \\
	5 & & \texttt{\hilight{commentblue}{// ...initialize...}}\\
	6 & & \texttt{publish(y);} \\
	7 & & \texttt{\hilight{brickred}{y->bar = ...;}} \\
\end{tabular}
\caption{A common execution pattern with {\tt malloc()} that produces false positive data race candidates.}
\label{fig:recycle}
\end{figure}
\begin{figure}[t]
	\small
\begin{tabular}{rll}
	& {\bf Thread 1} & {\bf Thread 2} \\
	1 & \texttt{publish(x);} & \\
	2 & \texttt{\hilight{brickred}{x->foo = ...;}} & \\
	3 & \texttt{\hilight{olivegreen}{free}(x);} \\
	4 & & \texttt{x2 = get\_published\_x();} \\
	5 & & \texttt{\hilight{commentblue}{// x's memory recycled}} \\
	6 & & \texttt{y~=~\hilight{olivegreen}{malloc}(sizeof *y);} \\
	7 & & \texttt{\hilight{brickred}{x2->foo = ...;}} \\
\end{tabular}
	\caption{If a single-pass \revision{Limited HB analysis}~discarded candidates matching the malloc-recycle pattern,
it would miss the bug in this adversarial program.}
\label{fig:recycle-bug}
\end{figure}

@@

\revision{This class of false positive is unique to heap-allocated memory among all ways threads could communicate.
By contrast, global memory has unlimited lifetime,
and message-passing primitives enforce an ordering which precludes the race. %(even under Limited HB).
Finally, note that as long as concurrent {\tt malloc} is implemented with an internal lock,
these false positives are of concern only under a Limited HB analysis (\sect{\ref{sec:overview-dr}}).
Nevertheless,
%our previous proof's
Theorem~\ref{thm:convergence}'s need for the Limited HB definition justifies our choice of it over full HB.
}
